Meta-analysis

### 2019-10-31 05_MetaAnalysis.Rmd
Editing file names

lm_rain <- read.csv("data/lmInSeasonRainfall.csv",stringsAsFactors = FALSE)

@@

plot(log(P_value) ~ days_from_plant, data = lm_data)
abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], col = "grey")
text(x = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], 
     y = log(max(lm_data$P_value))/0.95, 
     labels = paste("pvalue =",round(min(lm_data$P_value),2)),
     pos = 4)
plot(r_squared ~ days_from_plant, data = lm_data)
abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], col = "grey")
text(x = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], 
     y = max(lm_data$r_squared * 0.75), 
     labels = paste("Rsquared =",round(max(lm_data$r_squared),4)),
     pos = 2)

plot(estimate ~ days_from_plant, data = lm_data)
abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
```

>>>>

# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.20_50.110.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_10.30_60.95.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_20.40_80.110.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.30_50.80.csv",stringsAsFactors = FALSE)

@@
